Continuous Deductive Reasoning over Streamed RDF Data

### 2015-11-17 article.tex
small changes no time aaaaaaah

  % *brief* summary of state of the art (to be expanded in related work)
  Recent research has approached the task of stream reasoning from two different directions.
  %   RDF stream processing and reasoning
  The RDF stream processing community has proposed extensions to their continuous semantic query languages to support the \emph{iterative/recursive execution} of queries over the results of other queries \citep{C-SPARQL,EP-SPARQL,walavalkar08streamingkb}, in which each query expresses a rule in a logic program.
  This reflects precisely the approach to reasoning using Datalog in deductive databases, which has been characterised as the ``QUOTE'' \citep{DATALOG CHARACTERISATION}.
  Meanwhile, the reasoning community has explored the concept of continuously reasoning over streamed data in a variety of forms, primarily through a range of truth maintenance algorithms \citep{dred,inc-materialisation,stream-truth-maintenance}.

@@

WC-Datalog differs from conventional Datalog through the addition of
sources of continuously generated or reported facts (i.e streams), and
the application of windowing semantics over those sources,
thereby providing for the interpretation of WC-Datalog programs as
sequences of instantaneous states that may each be reduced to valid positive Datalog
programs.  As such, these states each inherit the semantics of
positive Datalog.  Furthermore, WC-Datalog provides for the continuous derivation
of entailments from this sequence of instantaneous states as a stream
of facts; the data model of these streams is subsumed by that currently proposed
by the RDF stream processing community\footnote{As presented at
\url{https://github.com/streamreasoning/RSP-QL/blob/master/Semantics.md}
on \mbox{03/11/2015}.}, thereby allowing the integration of WC-Datalog programs
into stream processing pipelines. Finally, we show that these streams may be
manipulated to retrieve the instantaneous sets of entailments produced
by the equivalent Datalog programs.

>>>>

  % *brief* summary of state of the art (to be expanded in related work)
  Recent research has approached the task of stream reasoning from two different directions.
  %   RDF stream processing and reasoning
  The RDF stream processing community has proposed extensions to their continuous semantic query languages to support the \emph{iterative/recursive execution} of queries over the results of other queries \citep{C-SPARQL,EP-SPARQL,walavalkar08streamingkb}, in which each query expresses a rule in a logic program.
  This reflects precisely the approach to reasoning using Datalog in deductive databases, in which queries may be executed on intensional relations whose definitions must be used in turn to query the database, recursing in this manner until base only extensional relations are queried.
  Meanwhile, the reasoning community has explored the concept of continuously reasoning over streamed data in a variety of forms, primarily through a range of truth maintenance algorithms \citep{dred,inc-materialisation,stream-truth-maintenance}.
  %%%FIXME
  NEED SOMETHING ON TIME-DECAY MODEL

@@

WC-Datalog differs from conventional Datalog through the addition of
sources of continuously generated or reported facts (i.e streams), and
the application of windowing semantics over those sources,
thereby providing for the interpretation of WC-Datalog programs as
sequences of instantaneous states that may each be reduced to valid positive Datalog
programs.  As such, these states each inherit the semantics of
positive Datalog.  Furthermore, WC-Datalog provides for the continuous derivation
of entailments from this sequence of instantaneous states as a stream
of time-annotated facts. The data model of these streams is subsumed by that currently proposed
by the RDF stream processing community\footnote{As presented at
\url{https://github.com/streamreasoning/RSP-QL/blob/master/Semantics.md}
on \mbox{03/11/2015}.}, in that each time-annotated fact may be expressed as a
RDF graph containing a single triple that is annotated with one or more
predicated timestamps; therefore integration of WC-Datalog programs
into stream processing pipelines is inherently supported. Finally, we show that these streams may be
manipulated to retrieve the instantaneous sets of entailments produced
by the equivalent Datalog programs.
